---
title: "Design evaluation and optimization with PFIM5.0"
fig: no crop
geometry: left=1mm, right=1mm, top=1mm, bottom=1mm, asymmetric
indent: TRUE
output:
  html_document:
    df_print: paged
    fig_caption: yes
    output: 
    highlight: textmate
  word_document: default
  pdf_document: default
header-includes: 
    - \usepackage{placeins}
    - \usepackage{indentfirst}
    - \usepackage{setspace}\doublespacing
    - \usepackage{lineno}
    - \linenumbers
---

```{r setup, include=FALSE, eval=TRUE}
knitr::opts_chunk$set(echo = TRUE,fig.retina = 2, fig.align="center")
options(kableExtra.latex.load_packages = FALSE)
```

## 1. Package PFIM5

- implemented using object-oriented programming
- objects have clear definition including class and argument definitions, inheritance, as well as argument checking, instantiation and implementation methods. 

- The version of this package is available from the Comprehensive R Archive Network at https://cran.r-project.org/web/packages/PFIM/index.html 

## 2. PFIM setup

The PFIM combines objects through a workflow to evaluate and optimize design. These objects describe the model equations as well as the model parameters, the arms, the designs etc. For more details one may see the additional detailed examples for design evaluation and optimization:

  https://cran.r-project.org/web/packages/PFIM/vignettes/Example01.html
  
  https://cran.r-project.org/web/packages/PFIM/vignettes/Example02.html

### The structural model: ModelODEquations()

The structural model is defined with the object **ModelODEquations( list(), list() )**:

- The first list defines the responses associated to the model responses.
- The second list defines the ODE equations of the model for each variable.

```{r ModelODEquations, eval=FALSE, echo=TRUE}
MyModelEquations = ModelODEquations(

  # list for the responses
  list( RespPK = expression( C1 ),
        RespPD = expression( C2 ) ),

  # list for the derivatives
  list( "Deriv_C1" = expression( dose_RespPK * ka / V  * exp( -ka * t ) - Cl * C1/V  ),
        "Deriv_C2" = expression( V*C1/Vm - Clm/Vm * C2 ) ) )
```

### The model parameters: ModelParameter()

Model parameters are defined with the object **ModelParameter( name, mu, omega, distribution, fixedMu, fixedOmega )** :

- name: a character string giving the name of the parameter
- mu: a numeric giving the value the fixed effects mu
- omega: a numeric giving the value of the variance effects omega
- distribution: the distribution of the parameters: LogNormalDistribution() for Log-Normal distribution or NormalDistribution() for a normal distribution
- fixedMu, fixedOmega: Boolean for estimating or not the fixed and random effects

```{r ModelParameter, eval=FALSE, echo=TRUE}
pka = ModelParameter( "ka", 
                      mu = 1.24,
                      omega =sqrt ( 0 ),
                      distribution = LogNormalDistribution(),
                      fixedMU = FALSE, 
                      fixedOmega = FALSE)
```

### The error model: Combined1()

Additive and proportional error model, are defined with the object **Combined1( sigma_inter, sigma_slope )**:

- sigma_inter: parameter for the additive part
- sigma_slope: parameter for the proportional part

```{r ModelError, eval=FALSE, echo=TRUE}
ModelErrorResponsePK = Combined1( sigma_inter = 0.6, sigma_slope = 0.07 )
```

### The response: Response()

- The model response is defined with the object **Response( name, model_error )** :
  - name: a string giving the name of the response
  - model_error: the model error of to the response   

```{r Response, eval=FALSE, echo=TRUE}
RespPK = Response( "RespPK", ModelErrorResponsePK )
```

### The arm: Arm()

- The arm is defined with the object **Arm( name, arm_size, cond_init )**:
  - name: a string for the name of the arm
  - arm_size: the size of the arm
  - condit_init: a list giving the initial condition of the model variables

```{r Arm, eval=FALSE, echo=TRUE}
arm1 = Arm( name = "Bras test", arm_size = 20, cond_init = list( "C1" = 0, "C2" = 0 ) )
```

### The sampling times: SamplingTimes()

- The sampling times are defined with the object **SamplingTimes( outcome, sample_time, initialTime )**
  - outcome: a string for the name of the response
  - sample_time: the vector of the sampling times
  - initialTime: values giving the initial sampling time
  
```{r SamplingTimes, eval=FALSE, echo=TRUE}
samplingTimesRespPK = SamplingTimes( outcome = "RespPK", 
                                     sample_time = c( 0.5, 170, 180, 192 ), initialTime = 0 )
```

### The administration: Administration()

- The administration is defined with the object **Administration( outcome, time_dose, amount_dose )**
  - outcome: a string for the name of the response
  - time_dose: the vector for the time doses
  - amount_dose: the vector for the amount of doses
  
```{r Administration, eval=FALSE, echo=TRUE}
administrationRespPK = Administration( outcome = "RespPK",
                                       time_dose = 24, 
                                       amount_dose = c(200) )
```
### The design: Design()

- The design is defined with the object  **Design( name )**
  - name: a string for the name of the design

```{r Design, eval=FALSE, echo=TRUE}
MyDesign = Design( "design1" )
```









