---
title: "Design evaluation and optimization with PFIM5.0"
fig: no crop
geometry: left=1mm, right=1mm, top=1mm, bottom=1mm, asymmetric
indent: TRUE
output:
  html_document:
    df_print: paged
    fig_caption: yes
    output: 
    highlight: textmate
  word_document: default
  pdf_document: default
header-includes: 
    - \usepackage{placeins}
    - \usepackage{indentfirst}
    - \usepackage{setspace}\doublespacing
    - \usepackage{lineno}
    - \linenumbers
author: ""
date: "`r paste( 'Date:' , Sys.Date())`"
---

```{r setup, include=FALSE, eval=TRUE}
knitr::opts_chunk$set(echo = TRUE,fig.retina = 2, fig.align="center")
options(kableExtra.latex.load_packages = FALSE)
```

# Package PFIM5

- implemented using object-oriented programming
- objects have clear definition including class and argument definitions, inheritance, as well as argument checking, instantiation and implementation methods. 

- The version of this package is available from the Comprehensive R Archive Network at https://cran.r-project.org/web/packages/PFIM/index.html with additional detailed examples for design evaluation and optimization:

  https://cran.r-project.org/web/packages/PFIM/vignettes/Example01.html
  
  https://cran.r-project.org/web/packages/PFIM/vignettes/Example02.html

# PFIM setup

PFIM requires the following objects to define a model:

 - **ModelODEquations()**: the structural model
 - **ModelParameter**, to define a model parameter
 - **Combined1()**: the model error
 
The PFIM combines together these objects through a pipeline to evaluate and optimize design.

## The structural model: ModelODEquations()

The structural model is defined with the object **ModelODEquations( list(), list() )**:

- The first list defines the responses associated to the model responses.
- The second list defines the ODE equations of the model for each variable.

```{r ModelODEquations, eval=FALSE, echo=TRUE}
MyModelEquations = ModelODEquations(

  # list for the responses
  list( RespPK = expression( C1 ),
        RespPD = expression( C2 ) ),

  # list for the derivatives
  list( "Deriv_C1" = expression( dose_RespPK * ka / V  * exp( -ka * t ) - Cl * C1/V  ),
        "Deriv_C2" = expression( V*C1/Vm - Clm/Vm * C2 ) ) )
```

## The model parameter: ModelParameter()

Model parameters are defined with the object **ModelParameter( name, mu, omega, distribution, fixedMu, fixedOmega )** :

- name: a character string giving the name of the parameter
- mu: a numeric giving the value the fixed effects mu
- omega: a numeric giving the value of the variance effects omega
- distribution: the distribution of the parameters: LogNormalDistribution() for Log-Normal distribution or NormalDistribution() for a normal distribution
- fixedMu, fixedOmega: Boolean for estimating or not the fixed and random effects

```{r ModelParameter, eval=FALSE, echo=TRUE}
pka = ModelParameter( "ka", 
                      mu = 1.24,
                      omega =sqrt ( 0 ),
                      distribution = LogNormalDistribution(),
                      fixedMU = FALSE, 
                      fixedOmega = FALSE)
```

## The residual error model

Additive and proportional error model, are defined with the object **Combined1( sigma_inter, sigma_slope )**:

- sigma_inter: parameter for the additive part
- sigma_slope: parameter for the proportional part

```{r ModelError, eval=FALSE, echo=TRUE}
ModelErrorResponsePK = Combined1( sigma_inter = 0.6, sigma_slope = 0.07 )
```

##  The response 

- The model response is defined with the object **Response( name, model_error )** :
  - name: a string giving the name of the response
  - model_error: the model error of to the response   

```{r Response, eval=FALSE, echo=TRUE}
RespPK = Response( "RespPK", ModelErrorResponsePK )
```

##  The arm

- The arm is defined with the object **Arm( name, arm_size, cond_init )**:
  - name: a string for the name of the arm
  - arm_size: the size of the arm
  - condit_init: a list giving the initial condition of the model variables

```{r Arm, eval=FALSE, echo=TRUE}
arm1 = Arm( name = "Bras test", arm_size = 20, cond_init = list( "C1" = 0, "C2" = 0 ) )
```

##  The sampling times

- The sampling times are defined with the object **SamplingTimes( outcome, sample_time, initialTime )**
  - outcome: a string for the name of the response
  - sample_time: the vector of the sampling times
  - initialTime: values giving the initial sampling time
  
```{r SamplingTimes, eval=FALSE, echo=TRUE}
samplingTimesRespPK = SamplingTimes( outcome = "RespPK", 
                                     sample_time = c( 0.5, 170, 180, 192 ), initialTime = 0 )
```

##  The administration 

- The administration is defined with the object **Administration( outcome, time_dose, amount_dose )**
  - outcome: a string for the name of the response
  - time_dose: the vector for the time doses
  - amount_dose: the vector for the amount of doses
  
```{r Administration, eval=FALSE, echo=TRUE}
administrationRespPK = Administration( outcome = "RespPK",
                                       time_dose = 24, 
                                       amount_dose = c(200) )
```
##  The design

- The design is defined with the object  **Design( name )**
  - name: a string for the name of the design

```{r Design, eval=FALSE, echo=TRUE}
MyDesign = Design( "design1" )
```
